Dynamic Graphics with the googleVis Package
========================================================

Using the **[googleVis](http://cran.r-project.org/web/packages/googleVis/index.html)** package, dynamic tables, maps, and motion charts can be created to allow the reader to interact with the content. Note that *gvis* objects, by default, contain `<html>` and `<body>` tags which should be removed since Knit HTML does this already. Passing `'chart'` to the print function accomplishes this.

<br>

### Interactive Chart and Map

```{r multiCharts, echo=TRUE, results='asis'}
suppressPackageStartupMessages(library(googleVis))
T <- gvisTable(Exports, 
               options=list(width=200, height=280))
G <- gvisGeoChart(Exports, locationvar="Country", colorvar="Profit",
                options=list(width=360, height=280, dataMode='regions'))
TG <- gvisMerge(T,G, horizontal=TRUE,
                tableOptions="bgcolor=\"#CCCCCC\" cellspacing=10")

print(TG, 'chart')
```

<br>

### R and Google Maps

```{r hurricaneAndrew, echo=TRUE, results='asis'}
## Hurricane Andrew (1992) storm track with Google Maps
AndrewMap <- gvisMap(Andrew, "LatLong" , "Tip", 
                     options=list(showTip=TRUE, showLine=TRUE, enableScrollWheel=TRUE,
                                  mapType='hybrid', useMapTypeControl=TRUE))

print(AndrewMap, 'chart')
```

<br>

### Dynamic Table

``` {r populationTable, echo=TRUE, results='asis'}
## Table with embedded links
PopTable <- gvisTable(Population, options=list(width=600, height=300, page='enable'))

print(PopTable, 'chart')
```

Return to [Using Markdown with RStudio](http://www.rstudio.org/docs/authoring/using_markdown)
